### 2023-03-17 annexes.qmd
update

```{=html}
<!--#https://github.com/quarto-dev/quarto-cli/discussions/1042-->
<style type="text/css">
caption, .table-caption {
  text-align: left;
}
</style>
```

```{r, poc database from traps}
#| label: tbl-poc-from-sediment-traps
#| tbl-cap: Compilation of POC flux measurements from sediment traps. Data taken from public databases listed on PANGAEA or extracted from articles (with the help of Frédéric Le Moigne and Meike Vogt). The number of measurements could be different from the original publication after data cleaning and potential removal of duplicates.
#| tbl-cap-location: bottom

>>>>

```{=latex}
%\includepdf[pages=1]{"/home/flo/dox/THESIS/bg-18-755-2021"}
```
```{=html}
<!--#https://github.com/quarto-dev/quarto-cli/discussions/1042-->
<style type="text/css">
caption, .table-caption {
  text-align: left;
}
</style>
```
```{r, poc database from traps}
#| label: tbl-poc-from-sediment-traps
#| tbl-cap: Compilation of POC flux measurements from sediment traps. Data taken from public databases listed on PANGAEA or extracted from articles (with the help of Frédéric Le Moigne and Meike Vogt). The number of measurements could be different from the original publication after data cleaning and potential removal of duplicates.
#| tbl-cap-location: bottom

### 2023-03-17 article3.qmd
update

In the first chapter, I explained the different steps that led to the creation of the embedded zooplankton classification model for the UVP6. However, I did not specify that in spite of the technical and energy constraints, the model was also due for April 2022 for a deployment of BGC-Argo floats in the Labrador Sea a month later. Once deployed, it was only a question of time before I could dig into the UVP6 and the OST data. In the meantime I asked myself, what could be a cool thing to do about those data? I already had some experience with BGC-Argo floats during my master's degree (study of the deep chlorophyll maximum in the Black Sea, see also the abstract of that paper in the annexes) and so while I was waiting for new profiles, I thought it would be useful to have a visualization tool in the form of a web app to investigate incoming data and already prepare the ground for the following study. Here is the link to the [web app](https://fricour.shinyapps.io/CARBON_REFINE/), which is still currently being automatically updated every day with new data (almost) live from the Labrador Sea and hopefully with other BGC-Argo floats equipped with the UVP6 and the OST to investigate carbon and particle fluxes in other regions. This study uses preliminary data (not even one year of data) and a new BGC-Argo float configuration hence more work should be addressed to better understand the dynamics of the system.

@@

p <- basemap(limits = c(-55,-40,55,65), bathymetry = T, lat.interval = 2.5, bathy.style = 'poly_blues')

>>>>

In the first chapter, I explained the different steps that led to the creation of the embedded zooplankton classification model for the UVP6. However, I did not specify that in spite of the technical and energy constraints, the model was also due for April 2022 for a deployment of BGC-Argo floats in the Labrador Sea a month later. Once deployed, it was only a question of time before I could dig into the UVP6 and the OST data. In the meantime I asked myself, what could be a cool thing to do about those data? I already had some experience with BGC-Argo floats during my master's degree (I published a paper on the study of the deep chlorophyll maximum in the Black Sea, [DOI: 10.5194/bg-18-755-2021](https://bg.copernicus.org/articles/18/755/2021/)) and so while I was waiting for new profiles, I thought it would be useful to have a visualization tool in the form of a web app to investigate incoming data and already prepare the ground for the following study. Here is the link to the [web app](https://fricour.shinyapps.io/CARBON_REFINE/), which is still currently being automatically updated every day with new data (almost) live from the Labrador Sea and hopefully with other BGC-Argo floats equipped with the UVP6 and the OST to investigate carbon and particle fluxes in other regions. This study uses preliminary data (not even one year of data) and a new BGC-Argo float configuration hence more work should be addressed to better understand the dynamics of the system.

@@

p <- basemap(limits = c(-55,-40,55,65), bathymetry = T, lat.interval = 2.5, bathy.style = 'poly_blues', bathy.alpha = .5)

### 2023-03-17 bcp_sequestration.qmd
update

>>>>

# Revisiting the BCP with the CONVERSE framework {#bcp-sequestration}

Initially, it was not intended that I work on this topic. As I will briefly explain in the general discussion, my attempts to find a global (or regional) relationship to derive POC fluxes from UVP5 size spectra failed constantly. Therefore, I was proposed to work on a new concept related to carbon sequestration. I was told I would be co-author, that it would be done quickly and that it was only about revising the carbon sequestration flux of the gravitational pump.

Why revise one pump when you can revise them all? 1 year and a half later, hundreds of emails, one promotion to first author, one negative review and one strong rebuttal, we are still on the road to publication. Here below is the revised version of our paper submitted in Nature Geoscience about the reassessment of the global sequestration (\> 100 years) of the BCP and its components by using a continuous approach to carbon storage as opposed to the common view of long-term sequestration below a fixed reference depth.

### 2023-03-17 observingCarbonCycle.qmd
update

1.  BGC-Argo floats equipped with a UVP6 and the zooplankton recognition algorithm are able to classify particles larger than 0.6 mm. However, these AUVs are limited in terms of their battery life. They are typically deployed for several years, which requires special attention to the energy consumption of each sensor. In @sec-uvp-ia, I will therefore describe the methodology used to develop the zooplankton classification model for the UVP6 accounting for energy limitations.
2.  Four BGC-Argo floats equipped with both a transmissometer and a UVP6 were deployed for the first time in the Labrador Sea in late May 2022 with the aim of observing POC export events due to the annual spring bloom. Unfortunately, it appears that the deployment occurred at the end of the spring bloom therefore we likely missed the major export events. In @sec-case-study-labrador-sea, I will therefore study the aftermaths of the spring bloom in terms of carbon fluxes estimated by both instruments. I will also compare the small (continuous) and big (stochastic) flux of particles as seen by transmissometers used as OSTs with PSDs measurements by UVP6s at three different drifting depths to investigate the relationship between the two instruments.
3.  Many studies have assumed that carbon sequestration only occurs in the deep ocean (typically 1000 m). In @sec-to-do, we reassess the global sequestration ($\geq$ 100 years) of the BCP and its components by using a continuous approach to carbon storage as opposed to the common view of long-term sequestration below a fixed reference depth.

>>>>

1.  BGC-Argo floats equipped with a UVP6 and the zooplankton recognition algorithm are able to classify particles larger than 0.6 mm. However, these AUVs are limited in terms of their battery life. They are typically deployed for several years, which requires special attention to the energy consumption of each sensor. In @sec-uvp6, I will therefore describe the methodology used to develop the zooplankton classification model for the UVP6 accounting for energy limitations.
2.  Four BGC-Argo floats equipped with both an OST and the UVP6 were deployed for the first time in the Labrador Sea in late May 2022 to study the dynamics of carbon fluxes and particle size distributions. In this chapter, I will explore the seasonality of the later and compare how the two sensors relate as two independent measurements of particle and carbon fluxes.
3.  Many studies have assumed that carbon sequestration only occurs in the deep ocean (typically 1000 m). In @bcp-sequestration, we reassess the global sequestration ($\geq$ 100 years) of the BCP and its components by using a continuous approach to carbon storage as opposed to the common view of long-term sequestration below a fixed reference depth.
